Extended Data

### 2021-12-03 doc/manuscript/Dow_manuscript_Nature.Rmd
add placeholder for data and code availability statements
#93
Update Dow_manuscript_Nature.Rmd

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$) and the DOY on which it occurred ($DOY_{g_{max}}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- and diffuse-porous species, which differ in growth phenology[@dorangeville_peak_2021]. These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).

@@

<!--MULTIVARIATE ANALYSIS METHODS-->
We used a multivariate model to test for joint effects of April and summer $T_{max}$ on RWI.
We began by testing univariate correlations of $T_{max}$ over three summer windows: June, June-July, and May-August. 
Having determined that, among these, June-July explained the most variation, we then analyzed the joint effects of April $T_{max}$ and June-July $T_{max}$ on RWI for each chronology independently using the base lm() function in R. 
Slopes and p-values for each chronology are given in `r chron_table`.

@@

>>>>

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$) and the DOY on which it occurred ($DOY_{g_{max}}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- (69 trees at SCBI and 138 trees at Harvard Forest) and diffuse-porous (54 trees at SCBI and 202 trees at Harvard Forest) species, which differ in growth phenology[@dorangeville_peak_2021]. These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).

@@

<!--MULTIVARIATE ANALYSIS METHODS-->
We used a multivariate model to test for joint effects of April and summer $T_{max}$ on RWI.
We began by testing univariate correlations of $T_{max}$ over three summer windows: June, June-July, and May-August. 
Having determined that, among these, June-July explained the most variation, we then analyzed the joint effects of April $T_{max}$ and June-July $T_{max}$ on RWI for each chronology independently using the base lm() function in R. 
Slopes and p-values for each chronology are given in `r chron_table`. Although some models may have benefited from data transformations, we determined that assumptions of normality and homoscedasticity were sufficiently met for the purposes of this analysis.

@@

# Data Availability Statement {-#Data}

# Code Availability Statement {-#Code}
